\begin{thebibliography}
	\bibitem{ekman} Экман П. Психология эмоций. Я знаю, что ты чувствуешь / П.~Экман. --- Питер, 2010.~--- 336~с.

	\bibitem{featureVector} Khandait S.~P. Automatic Facial Feature Extraction and Expression 
Recognition based on Neural Network / S.~P.~Khandait, R.~C~Thool, P.~D.~Khandait // International Journal of Advanced Computer Science and Applications. --- 2011. --- Vol. 2, No. 1.~--- P.~113--118.

	\bibitem{BPNN} Khandait S.~P. ANFIS and BPNN based Expression Recognition using HFGA for Feature Extraction / S.~P.~Khandait, R.~C.~Thool, P.~D.~Khandait // Bulletin of Electrical Engineering and Informatics.~--- 2013.~--- Vol. 2, No. 1.~--- P.~11--22.

	\bibitem{ANFIS}  Gomathi V. Human Facial Expression Recognition Using MANFIS Model / V. Gomathi, K. Ramar, A.~S.~Jeevakumar // Proceedings of World Academy of Science Engineering and Technology. --- 2009.~--- 38.~--- P.~338--342.

	\bibitem{HMM} I. Cohen. Emotion Recognition from Facial Expressions Using Multilevel HMM~/ I. Cohen, A. Garg, T.~S.~Huang // Neural Information Processing Systems.~--- 2000.

	\bibitem{template} Єфімов Г.~М. Технологія для моделювання та розпізнавання емоційної міміки на обличчі людини / Г.~М. Єфімов // Системи обробки інформації.~--- 2012.~--- С.~36--39.
	
	\bibitem{Jang} Jang J.-S.~R. Neuro-Fuzzy and Soft Computing: A Computational Approach to Learning and Machine Intelligence / J.-S.~R.~Jang, C.-T.~Sun, E.~Mizutani.~--- Prentice Hall, 1997.~--- 614~p.
	
	\bibitem{Haikin}  Хайкин С. Нейронные сети: полный курс : пер. с англ. / C.~Хайкин. --- [2-е изд.]. --- М.~: Издательский дом \invcommas{Вильямс}.~--- 2006.~--- 1104~с.
	
	\bibitem{FuzzySystem}  N. Tsapatsoulis. A Fuzzy System for Emotion Classification Based on the MPEG-4 Facial Definition Parameter Set / N. Tsapatsoulis, K. Karpouzis, G.~Stamou, F.~Piat, S.~Kollias // EURASIP Journal on Applied Signal Processing.~--- 2002.~--- P.~1021--1038.
	
	\bibitem{FaceReader} Noldus Information Technology. Face Reader homepage [Electronic Resource].~--- Mode of Access:
\url{http://www.noldus.com/human-behavior-research/products/facereader}

	\bibitem{eMotion} Visual Recognition. eMotion homepage [Electronic Resource]. --- Mode of Access: 
\url{http://www.visual-recognition.nl/eMotion.html}

	\bibitem{MMER} Face Analysis and Emotion Recognition [Electronic Resource]. --- Mode of Access: 
\url{http://www.amiproject.org/showcase/still-and-moving-image-processing/emotion-recognition}

	\bibitem{Affectiva} Affdex homepage [Electronic Resource]. --- Mode of Access:
\url{http://www.affdex.com/} 

	\bibitem{facsManual} Ekman P. Manual of the Facial Action Coding System (FACS) / P.~Ekman, W.~V.~Friesen.~--- Palo Alto~: Consulting Psychologists Press, 1978.
	
	\bibitem{facsInvGuide} Ekman P. Facial Action Coding System: Investigator’s Guide / P.~Ekman, W.~V.~Friesen.~--- Palo Alto~: Consulting Psychologists Press, 1978.

	\bibitem{Prata} С. Прата. Язык программирования С++. Лекции и упражнения : пер. с англ.~/ C.~Прата. --- 6-е изд. --- М.~: Издательский дом \invcommas{Вильямс}.~--- 2013.~--- 1248~с.
\end{thebibliography}
